Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-16 tex/MesnardoBarba2019.tex
Add paragraph about low-priority VMs
Also:

* Add low-priority pricing for the NC-series to the table.

\begin{table*}[!h]
    \renewcommand{\arraystretch}{1.5}
    \caption{NC series on Microsoft Azure. (Prices as of March 24, 2019, for CentOS or Ubuntu Linux Virtual Machines in the East US region.)}
    \label{tab:nc_series}
    \centering
    \begin{tabular}{cccccccc}
        Instance & cores & RAM & disk sizes & GPU & pay-as-you-go & 1-year reserved & 3-year reserved \\
        && (GiB) & (Gib) && (\$/hr) & (\$/hr) & (\$/hr) \\
        \hline
        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.5733 & 0.3996 \\
        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.1466 & 0.7991 \\
        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.2932 & 1.5981 \\
        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.5224 & 1.7578 \\
        \hline
    \end{tabular}
\end{table*}
\footnotetext{The NC24r configuration provides a low latency, high throughput network interface optimized for tightly coupled parallel applications.}

@@

>>>>

\begin{table*}[!h]
    \renewcommand{\arraystretch}{1.5}
    \caption{NC series on Microsoft Azure. (Prices as of March 24, 2019, for CentOS or Ubuntu Linux Virtual Machines in the East US region.)}
    \label{tab:nc_series}
    \centering
    \begin{tabular}{ccccccccc}
        Instance & cores & \begin{tabular}{@{}c@{}}RAM \\ (GiB) \end{tabular} & \begin{tabular}{@{}c@{}}disk sizes \\ (GiB) \end{tabular} & GPU & \begin{tabular}{@{}c@{}c@{}}pay-as-you-go \\ (dedicated) \\ (\$/hr) \end{tabular} & \begin{tabular}{@{}c@{}c@{}}pay-as-you-go \\ (low-priority) \\ (\$/hr) \end{tabular} & \begin{tabular}{@{}c@{}}1-year reserved \\ (\$/hr) \end{tabular} & \begin{tabular}{@{}c@{}}3-year reserved \\ (\$/hr) \end{tabular} \\
        \hline
        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.18 & 0.5733 & 0.3996 \\
        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 0.36 & 1.1466 & 0.7991 \\
        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 0.72 & 2.2932 & 1.5981 \\
        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 0.792 & 2.5224 & 1.7578 \\
        \hline
    \end{tabular}
\end{table*}
\footnotetext{The NC24r configuration provides a low latency, high throughput network interface optimized for tightly coupled parallel applications.}

@@

Microsoft Azure offers the possibility to take advantage of surplus capacity with ``low-priority'' virtual machines that are significantly cheaper than ``dedicated'' ones (\ref{tab:nc_series}).
For example, the low-priority \texttt{NC24r} instance has an hourly cost of $0.792$ USD, $5$ times cheaper than its dedicated counterpart.
However, the reader should keep in mind that low-priority may not be available for allocation or may be preempted at any time.
In fact, low-priority instances should be avoided for long-running MPI jobs in pools where inter-node communication is enabled.
We only used dedicated virtual machines to run our CFD software.
Moreover, our job tasks used a shared filesystems (GlusterFS on compute nodes) for I/O operations and Batch Shipyard will fail to create the pool if low-priority nodes are requested.
